Constant-round Blind Classical Verification of Quantum Sampling

### 2020-07-30 qpip0.tex
Fix bug

Now let $z_{true}$, as a mixed state, be correctly sampled from the $\SampBQP$ instance $D_x$,
and let $z_{ideal, i}=\tr(z_{good, i})z_{true}$.
We show that $z_{ideal, i}$ is close to $z_{good, i}$.
\begin{theorem}
	\label{thm:zgood-zideal}
	$\tr\abs{z_{good, i}-z_{ideal, i}}\leq O(\varepsilon)$
	\Ethan{This doesn't seem true; I think we get computational guarantees here at best?}
\end{theorem}
\begin{proof}
	For every $i\in [m]$ and every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for the naive $\QPIP_0$ Protocol, Protocol~\ref{proto:qpip0_naive}. Note that the prover only interact with the verifier in Step~\ref{step:urmila-in-naive} of Protocol~\ref{proto:qpip0_naive} where Protocol~\ref{proto:urmila4} is run, so we describe the prover's action in turns of the four rounds of communication in Protocol~\ref{proto:urmila4}.

@@

	By property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$ when the prover didn't abort. Since the prover's strategy is also efficient, by Lemma~\ref{lem:naive-qpip0-binding},
	$\tr\abs{z_{composite,i}-z_{ideal,i}}=O(\eps)$.
\end{proof}

>>>>

Now let $z_{true}$, as a mixed state, be correctly sampled from the $\SampBQP$ instance $D_x$,
and let $z_{ideal, i}=\tr(z_{good, i})z_{true}$.
We show that $z_{ideal, i}$ is close to $z_{good, i}$.
\begin{theorem}
	\label{thm:zgood-zideal}
	$z_{good, i}$ is $O(\eps)$-computationally indistinguishable to $z_{ideal, i}$.
\end{theorem}
\begin{proof}
	For every $i\in [m]$ and every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for the naive $\QPIP_0$ Protocol, Protocol~\ref{proto:qpip0_naive}. Note that the prover only interact with the verifier in Step~\ref{step:urmila-in-naive} of Protocol~\ref{proto:qpip0_naive} where Protocol~\ref{proto:urmila4} is run, so we describe the prover's action in turns of the four rounds of communication in Protocol~\ref{proto:urmila4}.

@@

	By property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$ when the prover didn't abort.
	Since the prover's strategy is also efficient, by Lemma~\ref{lem:naive-qpip0-binding},
	$z_{composite,}$ is $O(\eps)$-computationally indistinguishable to $z_{ideal, i}$.
\end{proof}
